Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-11-26 _tex/manuscript.tex
Built site for gh-pages

% author setup
\author*[1,2]{\fnm{Roman} \sur{Ludwig}}\email{roman.ludwig@usz.ch}\author[1,2]{\fnm{Yoel Perez} \sur{Haas}}\email{yoel.perezhaas@usz.ch}\author[1,2]{\fnm{Jan} \sur{Unkelbach}}\email{jan.unkelbach@usz.ch}
% affil setup
\affil[1]{\orgdiv{Department of Physics}, \orgname{University of
Zurich}}
\affil[2]{\orgdiv{Radiation Oncology}, \orgname{University Hospital
Zurich}}

@@

\textsubscript{Source:
\href{https://rmnldwg.github.io/bilateral-paper/manuscript-preview.html}{Article
Notebook}}

>>>>

% author setup
\author*[1,2]{\fnm{Roman} \sur{Ludwig}}\email{roman.ludwig@usz.ch}\author[1,2]{\fnm{Yoel Perez} \sur{Haas}}\email{yoel.perezhaas@usz.ch}\author[3]{\fnm{Sergi} \sur{Benavente}}\email{sergi.benavente@vallhebron.cat}\author[2]{\fnm{Panagiotis} \sur{Balermpas}}\email{panagiotis.balermpas@usz.ch}\author[1,2]{\fnm{Jan} \sur{Unkelbach}}\email{jan.unkelbach@usz.ch}
% affil setup
\affil[1]{\orgdiv{Physics}, \orgname{University of Zurich}}
\affil[2]{\orgdiv{Radiation Oncology}, \orgname{University Hospital
Zurich}}
\affil[3]{\orgdiv{Radiation Oncology}, \orgname{University Hospital Vall
d'Hebron}}

@@

\textsubscript{Source:
\href{https://rmnldwg.github.io/bilateral-paper/manuscript.qmd.html}{Article
Notebook}}
